---
title: "RR2"
author: "Nancy"
date: "2020/6/28"
output: html_document
---

Reproducible-Research-Course-Project 2
========================================

1.reading in the dataset and/or processing the data

```{r readingdata,echo=TRUE}
fileUrl<-"https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(fileUrl,destfile ="C:/Users/123/Desktop/data/activity.zip")
unzip("C:/Users/123/Desktop/data/activity.zip",exdir = "C:/Users/123/Desktop/data")
activity<-read.csv("C:/Users/123/Desktop/data/activity.csv")
head(activity)
```

2.Histogram of the total number of steps taken each day
```{r histogram,echo=TRUE}
step_sum<-tapply(activity$steps,activity$date,sum)
hist(step_sum,breaks = 10,col="blue",xlim = c(0,25000),ylim =c(0,20),main="Total Number of Steps Taken Each Day")
```

3.Mean and median number of steps taken each day
```{r meanandmedian,echo=TRUE}
mean<-mean(step_sum,na.rm = TRUE)
median<-median(step_sum,na.rm = TRUE)
```

The mean of the steps is `r mean` and the median of the steps is `r median`.

4.Time series plot of the average number of steps taken
```{r timeseriesplot,echo=TRUE,fig.length=4}
activity<-transform(activity,interval=factor(interval))
stepsPerInterval<-tapply(activity$steps,activity$interval,mean,na.rm=TRUE)
plot(names(stepsPerInterval),stepsPerInterval,type = "l",main = "Average Steps Per Interval",xlab = "5-minute Interval",ylab = "Average Steps")
```

5.The 5-minute interval that contains the maximum steps 
```{r 5minuteinterval,echo=TRUE}
maximum<-names(which.max(stepsPerInterval))
```
The 5-minute interval that contains the maximum steps is `r maximum`.

6.Total number of missing values
```{r missingvalues,echo=TRUE}
missing_values<-nrow(activity[is.na(activity),])
```

Total number of missing values is `r missing_values`.

7.Devise a strategy for filling in all of the missing values in the dataset and Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r filledmissingvalues,echo=TRUE}
newActivity<-activity
newActivity[is.na(newActivity$steps),"steps"]<-mean(newActivity$steps,na.rm=TRUE)
head(newActivity)
```
8.Histogram of the total number of steps taken each day for the new dataset.
```{r histogramofnewdataset,echo=TRUE}
new_step_sum<-tapply(newActivity$steps,newActivity$date,sum)
hist(new_step_sum,col = "orange",breaks=10,main="Total Steps Taken Each Day",xlab = "Steps",xlim=c(0,25000),ylim=c(0,30))
```

9.Mean and median of the number of steps taken each day for the new dataset
```{r meanandmedianfornewdataset,echo=TRUE}
newMean<-mean(new_step_sum,na.rm=TRUE)
newMedian<-median(new_step_sum,na.rm=TRUE)
```

After imputing the missing values, the new mean keeps unchanged while the new median increases when compare to the original dataset "activity". In general, the changing is negligible.

10.Create a new factor variable in the dataset with two levels. 
```{r newvariable,echo=TRUE}
newActivity$date<-as.POSIXct(newActivity$date)
newActivity$day<-"Weekdays"
newActivity$day[weekdays(newActivity$date) %in% c("Saturday", "Sunday")] <- "Weekend"
```

11.Make a panel plot containing a time series plot.
```{r,echo=TRUE}
par(mfrow=c(2,1),mar=c(4,4,2,1))
Weekend<-subset(newActivity,day=="Weekend")
WeekendMean<-tapply(Weekend$steps,Weekend$interval,mean)
Weekdays<-subset(newActivity,day=="Weekdays")
WeekdaysMean<-tapply(Weekdays$steps,Weekdays$interval,mean)
plot(names(WeekendMean),WeekendMean,type="l",ylim=c(0,250),xlab = "5-minute-Interval",ylab = "Average Steps",main = "Average Steps on Weekend")
plot(names(WeekdaysMean),WeekdaysMean,type = "l",ylim=c(0,250),xlab = "5-minute-Interval",ylab = "Average Steps",main = "Average Steps on Weekdays")
```